### 2018-09-24 ApproxComp/TKDE/coverletter.tex

I would like to request you to consider the attached manuscript entitled ``Approximate Computation for Big Data Analytics'' for publication in Communications of the ACM  as a contributed article.

@@

Below please find the names and email addresses of possessible appropriate reviewers:

\bi
\item[(1)] Prof. Sihem Amer-Yahia: Sihem.Amer-Yahia@imag.fr

\item[(2)]  Prof. Evaggelia Pitoura: pitoura@cs.uoi.gr

\item[(3)]  Prof. Lei Chen: leichen@cse.ust.hk

\item[(4)]  Prof. Feifei Li: lifeifei@cs.utah.edu
\ei

>>>>

I would like to request you to consider the attached manuscript entitled ``Approximate Computation for Big Data Analytics'' for publication in IEEE Transactions on Knowledge and Data Engineering a concise article.

@@
